Preregistered as Code: Gender differences in Machiavellianism

### 2021-09-17 preregistration.Rmd
Necessary deviations from the preregistration - reversed items

```{r, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
real_data <- here::here("data", "data.csv")
simulated <- !fs::file_exists(real_data)
if(simulated){
  cat("\\textcolor{red}{The results are based on simulated data and must not be
      interpreted. They only serve to illustrate the result of the preregistered
      code.}")
  set.seed(1234)
  mach <- simulate_data(900, 8, 0.3, 10)
} else {
  mach <- readr::read_delim(real_data, delim = "\t")
  # only keep MACH items + gender
  mach <- dplyr::select(mach, dplyr::matches("^Q\\d+A$"), gender)
  # code gender according to codebook (3 would be other)
  mach <-
    dplyr::mutate(mach, gender = factor(
      gender,
      levels = 1:2,
      labels = c("male", "female")
    ))
}
```
<!--end-results-->

>>>>

```{r, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
real_data <- here::here("data", "data.csv")
simulated <- !fs::file_exists(real_data)
if(simulated){
  cat("\\textcolor{red}{The results are based on simulated data and must not be
      interpreted. They only serve to illustrate the result of the preregistered
      code.}")
  set.seed(1234)
  mach <- simulate_data(900, 8, 0.3, 10)
} else {
  mach <- readr::read_delim(real_data, delim = "\t", na = c("", "NA", "NULL"))
  # only keep MACH items + gender
  mach <- dplyr::select(mach, dplyr::matches("^Q\\d+A$"), gender)
  # code gender according to codebook (3 would be other)
  mach <-
    dplyr::mutate(mach, gender = factor(
      gender,
      levels = 1:2,
      labels = c("male", "female")
    ))
  # some items are reversed, see https://core.ac.uk/download/pdf/38810542.pdf
  reversed_nr <- c(1, 15, 2, 12, 4, 11, 14, 19)
  reversed <- stringr::str_c("Q", reversed_nr, "A")
  mach <- dplyr::mutate(mach, dplyr::across(one_of(reversed), ~ 6 - .x))
}
```
<!--end-results-->
